### 2019-11-13 latex/vnhcs.tex
Moved Hamiltonian review to VNHCs again

%/----- Motivation -----/%
\subsection{Motivation}
TODO: Why do we bother with Hamiltonian? Why can't we do virtual nonholonomic constraints in Lagrangian?

@@

Theorem \ref{thm:equation_for_pa} guarantees that, on \(\Gamma\), \(q_a\) is a
parameterized completely by \((q_u,p_u)\). Hence, the zero-dynamics on
\(\Gamma\) are always two-dimensional regardless of the original dimension
\(n\).
%/========== /Virtual Nonholonomic Constraints ==========/% vim: set ts=4 sw=4
%sts=0 et ffs=unix :

>>>>

%/----- Motivation -----/%
\subsection{Motivation}
Suppose one wishes to set a constraint that depends on both the configuration
and the velocity.
TODO: Why do we bother with Hamiltonian? Why can't we do virtual nonholonomic 
constraints in Lagrangian?

\subsection{Review: Hamiltonian Systems}
\textbf{TODO: What is a Hamiltonian system and why does it matter?}

One can compute the Hamiltonian of the Lagrangian (\ref{eqn:lagrangian}) by 
performing a Legendre transform on the Lagrangian. 
First, define the conjugate of momenta for \(q\) by 
\begin{equation*}
p = \frac{\partial \mathcal{L}}{\partial \dot{q}} \in \mathbb{R}^n
\end{equation*}
Then, the Legendre transform is performed by taking
\begin{equation*}
\mathcal{H}(q,p) = p^T \dot{q} - \mathcal{L}(q,\dot{q})
\end{equation*}
It is easy to verify that the Hamiltonian for system (\ref{eqn:lagrangian}) is 
given by the total mechanical energy (\ref{eqn:hamiltonian}).
\begin{equation}\label{eqn:hamiltonian}
\mathcal{H}(q,p) = E(q,p) = \frac{1}{2} p^T M^{-1}(q) p + V(q)
\end{equation}

The equations of motion for the system in Hamiltonian coordinates is given by
\begin{align}\label{eqn:hamiltionian_eom}
\begin{split}
\dot{q} &= \frac{\partial \mathcal{H}}{\partial p} = M^{-1}(q) p \\
\dot{p} &= -\frac{\partial \mathcal{H}}{\partial q} + B \tau
\end{split}
\end{align}

\textbf{Why bother looking at Hamiltonian systems? What is the intuition behind
these equations of motion?}

\subsection{Hamiltonian Virtual Nonholonomic Constraints}
While VHCs are still possible in the Hamiltonian framework, the assumptions
required to make this work are slightly different. To see this, let us look back
to the derivation which led to the error dynamics (\ref{eqn:vhc_error_dynamics})
and attempt to reconstruct this in Hamiltonian coordinates.

@@

Theorem \ref{thm:equation_for_pa} guarantees that, on \(\Gamma\), \(q_a\) is a
parameterized completely by \((q_u,p_u)\). Hence, the zero-dynamics on
\(\Gamma\) are always two-dimensional regardless of the original dimension
\(n\).

%---------- Hamiltonian VHCS ---------%
\subsection{Hamiltonian Virtual Holonomic Constraints}
\textbf{TODO: Why can we not do the standard VHC approach for Hamiltonian? 
Show how to use the above to make it work}

%/========== /Virtual Nonholonomic Constraints ==========/% 
% vim: set tw=80 ts=4 sw=4 sts=0 et ffs=unix :
